Performance of two different ontological and data access methods

### 2015-03-05 cold2014/magnus.tex
Added more on how the levels are set
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@756 43ef1190-90fd-4dd7-a769-d0121f02b80e
Added more on how the levels are set
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@757 43ef1190-90fd-4dd7-a769-d0121f02b80e
Remove figures
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1042 43ef1190-90fd-4dd7-a769-d0121f02b80e

\subsubsection{Experiment with ten factors}
The last experiment we did was a ten factor experiment. The goal here
was to see which factors would be deemed significant in a complete car
model search. With the results from this experiment we could discuss
several aspects of using the different ontologies.  
With 10 factors, we have $2^{10}$, which is quite large for a full
factorial experiment.
To determine the levels of each factor, we calculated the average value 
of each factor present in the data sets. % TODO: more on this.

@@

\begin{figure}%{r}{0.65\textwidth}
\begin{center}
\vspace{-15pt}
 \includegraphics[width=8.5cm, height=7cm]{2factorfinal.pdf}
  \caption{Resulting graph for the three factor experiment}\label{3factorGraph}
\vspace{-10pt}
\end{center}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=14cm]{10factorAvarageDanielPlot.pdf}
  \caption{Resulting graph for the ten factor experiment}\label{10factorGraph}
\end{figure}

>>>>

\subsubsection{Experiment with ten factors}
The last experiment we did was a ten factor experiment. The goal here
was to see which factors would be deemed significant in a complete car
model search. With the results from this experiment we could discuss
several aspects of using the different ontologies.  
With 10 factors, we have $2^{10}$, which is quite large for a full
factorial experiment.
To determine the levels of each factor, we calculated the average value 
of each factor present in the data sets. The two levels of each factor would then 
represent either values over or under the average. This was done to hit 
as many values in the data sets as possible. % TODO: more on this.

@@

@@
